---
title: "R Notebook"
output: html_notebook
---

```{r}
library(lubridate)
library(dplyr)
library(ggplot2)
library(reshape2)
library(survminer)
library(survival)
library(stringr)
library(zoo)
library(ggthemes)
source("src/helpers.R")
```


```{r}
input_csv <- "/Users/henry/Mastodon C/witan.cic/data/scc/2020-12-04/suffolk-scrubbed-episodes-20201203.csv"
data <- read.csv(input_csv)
data$report_date <- ymd(data$report_date)
data$ceased <- ymd(data$ceased)

data <- data %>% mutate(birthday = ymd(paste0(DOB, "-01")))
```

What proportion of first episodes for a given child in the data are not marked to show they are first entry to care? 

```{r}

ggplot(data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1), aes(RNE)) + geom_bar()

prop.table(table((data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>% mutate(RNE_type = if_else(RNE == "S", "Start", "Not start")))$RNE_type)) * 100

prop.table(table((data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>% mutate(RNE_type = if_else(RNE == "S", "Start", "Not start")))$RNE)) * 100

data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>% mutate(age_entry = factor(year_diff(birthday, report_date), levels = 0:18)) %>%
  ggplot(aes(age_entry, fill = RNE)) + geom_bar(position = "fill")

data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>% mutate(report_year = factor(year(report_date), levels = 1995:2020), age_entry = factor(year_diff(birthday, report_date), levels = 0:18)) %>%
  ggplot(aes(age_entry, fill = RNE)) + geom_bar(position = "fill") + facet_wrap(vars(report_year))

```
Chart above demonstrates that we are likely missing the initial episode(s) from all children entering prior to 2009. This means we are unlikely to see the true likelihood of a child remaining in care for more than 10 years.


```{r}
## Ruth data

ruth_main_csv <- "/Users/henry/Mastodon C/witan.cic/data/scc/2021-01-07/2020-12-10 Mastodon 19-20 CiC data + PR code + URN unencrypted.csv"
ruth_header_csv <- "/Users/henry/Mastodon C/witan.cic/data/scc/2021-01-07/2020-12-10 Mastodon 19-20 CiC data + PR code + URN unencrypted header row.csv"
ruth_main <- read.csv(ruth_main_csv)
ruth_header <- read.csv(ruth_header_csv)

ruth_data <- ruth_main %>% inner_join(ruth_header %>% unique) %>%
  mutate(report_date = parse_date_time(DECOM, orders = "%d/%m/%Y"), ceased = parse_date_time(DEC,orders = "%d/%m/%Y"),
         date_entry = parse_date_time(D_LAST_POC, orders = "%d/%m/%Y"),
         ID = Anonymised.id)

ruth_data <- ruth_data %>% mutate(birthday = ymd(paste0(DOB, "-01")))

```

We want to show that all children who don't have an initial S RNE have an earlier start date.

```{r}
table((ruth_data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>%
  filter(RNE != "S") %>% mutate(earlier_date_entry = date_entry < report_date))$earlier_date_entry)

ruth_data %>% arrange(ID, report_date) %>% group_by(ID) %>% slice(1) %>%
  filter(RNE != "S") %>% mutate(missing_duration = day_diff(date_entry, report_date)) %>%
    ggplot(aes(missing_duration)) + geom_histogram(bins = 50)

```

Compare total durations of children in care both with and without Ruth's data.

```{r}
# Convert ruth's data to periods

period_durations <- ruth_data %>% assoc.period.id %>% arrange(report_date) %>% group_by(period_id) %>%
  summarise(imputed_period_duration = day_diff(min(report_date), max(ceased)) / 365.0,
            actual_period_duration = day_diff(min(date_entry), max(ceased)) / 365.0) %>% ungroup

period_durations %>% mutate(period_difference = actual_period_duration - imputed_period_duration) %>%
  ggplot(aes(period_difference)) + geom_histogram()

duration_cdfs <- rbind(period_durations %>% filter(!is.na(imputed_period_duration)) %>% mutate(label = "imputed", q = ecdf(imputed_period_duration)(imputed_period_duration), duration = imputed_period_duration), period_durations %>%  filter(!is.na(actual_period_duration)) %>% mutate(label = "actual", q = ecdf(actual_period_duration)(actual_period_duration), duration = actual_period_duration))
                                       
duration_cdfs %>%
  ggplot(aes(duration, q, colour = label)) +
  scale_y_continuous(breaks = seq(0,1,by = 0.05)) +
  scale_x_continuous(breaks = seq(0,18)) +
  geom_line()

child_durations <- ruth_data %>% arrange(report_date) %>% group_by(ID) %>%
  summarise(RNE = RNE[1],
            min_report_date = min(report_date),
            max_ceased = max(ceased),
            min_date_entry = min(date_entry),
            imputed_period_duration = day_diff(min(report_date), max(ceased)) / 365.0,
            actual_period_duration = day_diff(min(date_entry), max(ceased)) / 365.0) %>% ungroup

child_durations %>% filter(is.na(max_ceased)) %>% mutate(group = min_report_date == min_date_entry) %>%
  group_by(group) %>% summarise(n = n())

child_duration_cdfs <- rbind(child_durations %>% filter(!is.na(imputed_period_duration)) %>% mutate(label = "imputed", q = ecdf(imputed_period_duration)(imputed_period_duration), duration = imputed_period_duration), child_durations %>%  filter(!is.na(actual_period_duration)) %>% mutate(label = "actual", q = ecdf(actual_period_duration)(actual_period_duration), duration = actual_period_duration))
                                       
child_duration_cdfs %>%
  ggplot(aes(duration, q, colour = label)) +
  scale_y_continuous(breaks = seq(0,1,by = 0.05)) +
  scale_x_continuous(breaks = seq(0,18)) +
  geom_line()



```

```{r}
ruth_data
# 1,944 episodes

length(unique((ruth_data %>% assoc.period.id)$period_id))
# 1,239

length(unique(ruth_data$ID))
# 1,239

ruth_data %>% group_by(ID) %>% summarise(min_report_date = min(report_date),
                                         min_date_entry = min(date_entry),
                                         day_diff = day_diff(min_date_entry, min_report_date)) %>%
  filter(abs(day_diff) > 700)


ruth_data %>% group_by(ID) %>% summarise(min_report_date = min(report_date),
                                         min_date_entry = min(date_entry),
                                         diff = min_date_entry != min_report_date,
                                         report_year = year(min_report_date)) %>%
  group_by(report_year, diff) %>% summarise(n = n()) %>%
  ggplot(aes(report_year, n, fill = diff)) + geom_bar(stat = "identity", position = "fill")
```
```{r}


child_durations <- data %>% inner_join(ruth_data %>% dplyr::select(ID, date_entry), by = "ID") %>% assoc.period.id %>% arrange(report_date) %>% group_by(period_id) %>%
  summarise(RNE = RNE[1],
            min_report_date = min(report_date),
            max_ceased = max(ceased),
            min_date_entry = min(date_entry),
            imputed_period_duration = day_diff(min(report_date), max(ceased)) / 365.0,
            actual_period_duration = day_diff(min(date_entry), max(ceased)) / 365.0) %>% ungroup

child_durations %>% filter(is.na(max_ceased)) %>% mutate(group = min_report_date == min_date_entry) %>%
  group_by(group) %>% summarise(n = n())

child_duration_cdfs <- rbind(child_durations %>% filter(!is.na(imputed_period_duration)) %>% mutate(label = "imputed", q = ecdf(imputed_period_duration)(imputed_period_duration), duration = imputed_period_duration), child_durations %>%  filter(!is.na(actual_period_duration)) %>% mutate(label = "actual", q = ecdf(actual_period_duration)(actual_period_duration), duration = actual_period_duration))
                                       
child_duration_cdfs %>%
  ggplot(aes(duration, q, colour = label)) +
  scale_y_continuous(breaks = seq(0,1,by = 0.05)) +
  scale_x_continuous(breaks = seq(0,18)) +
  geom_line()

```

## Generate bar chart of expected duration in care by age of entry

Using survival analysis, we want to come up with the expected care duration by age of entry.

```{r}

max_date <- max(max(data$ceased, na.rm = TRUE), max(data$report_date))

d <- 0.5

survdata <- data %>%
  left_join(ruth_data %>% select(ID, date_entry), by = "ID") %>%
  assoc.period.id %>%
  mutate(birthday = as.Date(paste0(DOB, "-01"))) %>%
  group_by(period_id) %>%
  summarise(date_entry = date_entry[1],
            DOB = DOB[1],
            implied_duration = day_diff(min(report_date), coalesce(max(ceased), max_date)),
            actual_duration = if_else(date_entry < min(report_date),
                                            day_diff(date_entry, coalesce(max(ceased), max_date)),
                                            implied_duration),
            RNE = RNE[1],
            event = !is.na(max(ceased)),
            join_age = year_diff(min(birthday), min(report_date)),
            join_age_days = day_diff(min(birthday), max(report_date)))

  ## Implied data
  fit <- survfit(Surv(implied_duration, event) ~ join_age, data = survdata)
  long.quantile <- reshape2::melt(stats::quantile(fit, probs = seq(0,0.999,length.out = 1000))$quantile) %>%
    mutate(join_age = as.integer(str_replace(Var1, "join_age=", ""))) %>%
    select(-1) %>%
    as.data.frame
  colnames(long.quantile) <- c("quantile", "duration", "join_age")
  
  wide.cdf <- dcast(join_age ~ quantile, data = long.quantile, drop = FALSE, value.var = "duration")
  colnames(wide.cdf)
  wide.cdf <- cbind(wide.cdf, data.frame(`100` = apply(wide.cdf, 1, max, na.rm = TRUE)))
  wide.cdf.imputed <- as.data.frame(t(na.approx(t(wide.cdf))))
  colnames(wide.cdf.imputed) <- c("join_age", seq(0, 1000, length.out = ncol(wide.cdf.imputed) - 1))
  long.cdf.imputed <- melt(wide.cdf.imputed, id.vars = "join_age")
  
  granularity <- 1 # How many data points per year
  
  long.pdf <- long.cdf.imputed %>%
    mutate(age_exit = join_age + (value / 365.0)) %>%
    mutate(age_exit = floor(age_exit * granularity) / granularity) %>%
    group_by(join_age, age_exit) %>%
    summarise(q = min(as.numeric(as.character(variable)))) %>%
    mutate(p = q - coalesce(lag(q), 0.0)) %>%
    mutate(p = p * 100 / sum(p)) %>%
    ungroup
  
  ggplot(long.pdf, aes(age_exit, p)) + geom_bar(stat = "identity") + facet_wrap(vars(join_age))

```
```{r}
  ## Actual data from Ruth
  fit <- survfit(Surv(actual_duration, event) ~ join_age, data = survdata)
  long.quantile <- reshape2::melt(stats::quantile(fit, probs = seq(0,0.999,length.out = 1000))$quantile) %>%
    mutate(join_age = as.integer(str_replace(Var1, "join_age=", ""))) %>%
    select(-1) %>%
    as.data.frame
  colnames(long.quantile) <- c("quantile", "duration", "join_age")
  
  wide.cdf <- dcast(join_age ~ quantile, data = long.quantile, drop = FALSE, value.var = "duration")
  colnames(wide.cdf)
  wide.cdf <- cbind(wide.cdf, data.frame(`100` = apply(wide.cdf, 1, max, na.rm = TRUE)))
  wide.cdf.imputed <- as.data.frame(t(na.approx(t(wide.cdf))))
  colnames(wide.cdf.imputed) <- c("join_age", seq(0, 1000, length.out = ncol(wide.cdf.imputed) - 1))
  long.cdf.imputed <- melt(wide.cdf.imputed, id.vars = "join_age")
  
  granularity <- 1
  
  long.pdf <- long.cdf.imputed %>%
    mutate(age_exit = join_age + (value / 365.0)) %>%
    mutate(age_exit = floor(age_exit * granularity) / granularity) %>%
    group_by(join_age, age_exit) %>%
    summarise(q = min(as.numeric(as.character(variable)))) %>%
    mutate(p = q - coalesce(lag(q), 0.0)) %>%
    mutate(p = p * 100 / sum(p)) %>%
    ungroup
  
  ggplot(long.pdf, aes(age_exit, p)) + geom_bar(stat = "identity") + facet_wrap(vars(join_age))
```



